% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (doucture helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage{setspace}
\usepackage{url}
\usepackage{hyperref}
\begin{document}

\name{Zhechen Min}
% \address used twice to have two lines of address
\address{+1-647-970-3661,   owen200104@gmail.com}
\address{404\#105 The Queensway, Toronto Canada, M6S 5B5}
\begin{resume}
\section{SKILLS} 
	{\sl Proficient in } 
						\begin{itemize}
						\item Algorithms and Data structures
						\item Python, Java,  C/C++ and STL
						\item Vim
						\end{itemize}
    {\sl Familiar with }
						\begin{itemize}
						\item Linux(Debian, Arch)
						\item HTML, CSS, JavaScript, Pascal, Swift
						\item Eclipse, Git, Subversion, Perforce, \LaTeX
						\end{itemize}
 	{\sl Know about } 
					\begin{itemize}
					\item PHP, Ruby, MySQL, MIPS, 	
					\item jQuery, eXist, Django, Ruby on Rails, SpriteKit
					\end{itemize}

\section{Work Experience}
\begin{itemize}
\item {\sl Amazon.com, Inc, Toronto, Canada}\\
	Software Development Engineer, Collating and Picking Optimization \\
Jul. 2013 - Jul. 2014
\item {\sl Research In Motion Ltd, Waterloo, Canada}\\
	Software Developer, Mobile Voice System(MVS) Session Management \\
Jan. 2012 - Apr. 2012
\item {\sl MRX Solutions Corp, Vancouver, Canada}\\
 QA / Product Development \\
Sep. 2011 - Dec. 2011
\end{itemize}


\section{Honors}
{\sl ACM/ICPC}
\begin{itemize}
\item Ranked 8/75 in The 2010 ACM/ICPC Pacific Northwest Regional Contest	
\item Ranked 9/77 in The 2009 ACM/ICPC Pacific Northwest Regional Contest	
\item Ranked 2nd in The 6th Zhejiang Provincial Collegiate Programming Contest 
\item Ranked 3rd in The 10th Zhejiang University Programming Contest 
\item Brozen medal in The 2008 ACM/ICPC Asia Hangzhou Regional Contest 
\item Brozen medal in The 2008 ACM/ICPC Asia Beijing Regional Contest   

\end{itemize}
{\sl Olympiad in Informatics}
\begin{itemize}
\item The first  prize in The 2007 National Olympiad in Informatics in Zhejiang Provinces China 
\item The second prize in The 2006 National Olympiad in Informatics in Zhejiang Provinces China
\end{itemize}


\section{Personal Projects and Other Experience}
\begin{itemize}
\item {\bf Square} An iOS Game based on Swift and SpriteKit.
\item {\bf My family Tree} An SNS family tree website using Django as backend.
\item {\bf alfred-Cal} A calendar gadget based on Alfred.
\item {\bf alfred-Forvo} A pronunciation gadget based on Alfred. 
\item {\bf alfred-IME} An Input Method gadget based on Google Input Tools and Alfred.
\item {\bf alfred-Messager} An Instant Messager gadget based on Alfred.
\item {\bf Lazyfill} A vim plugin that generates formated code based on file path and custom templates.

\item {\bf Decafe Compiler} A Decafe Compiler implemented by C++ and MIPS.
\item {\bf Topcoder.com Bug Races}
\item {\bf Other Open Source Projects contributed to}
	\begin{itemize}
		\item {\bf alfred-Workflow} A helper library in Python for developers of workflows for Alfred.
		\item {\bf alfred-Weather} A weather information gadget based on Alfred.
	\end{itemize}
\end{itemize}
\section{EDUCATION}
				{\sl Simon Fraser University, Canada}\\
				Bachelor of Computer Science 
				2009 - 2013 \\
%				\begin{spacing}{1.0}
%				\end{spacing}
				\\
				{\sl Zhejiang University, China} \\
				Bachelor of Computer Science	
				2007 - 2009  
%				\begin{spacing}{1.0}
%				\end{spacing}

\end{resume}
\end{document}







